---
title: "Finance & Time Series"
author: "Robert Arcaleanu"
format:
  html: 
    theme: united
server: shiny
toc: true
execute: 
  echo: false

---

# Introduction

This project is intended to demonstrate my knowledge on the following topics, but do not make decisions based on the results presented in the following sections:

- Stock Market - still working on it ;)
- Timeseries
- Data Analytics


```{r, include=FALSE}
packages <- list("data.table","ggplot2", "quantmod", "forecast","prophet",
                 "tidymodels", "lubridate", "tidyquant", "shiny", "plotly")
lapply(packages, require, character.only = T)
library(ggplot2)
```

# Quantitative Fianance



Select the stock and the time frame you want to analyse:
```{r}
inputPanel(
  shiny::textInput("stock", "Select Stock", "PG")
)

fluidPage(
  dateRangeInput("dates", label = "Date range",  start = Sys.time() - 24*365*3600)
)

```

```{r}
plotlyOutput("distPlot")
```





## Calculating and Comparing rates of return


## Measuring investment risk


# Time Series

In this section we try to forecast the stock value. The analysis below is only taking into account some of the most well-known techniques for time series. However, financial aspects are not considered.



## ARIMA

## Prophet


## Neural Networks 

## Ensemble


```{r}
#| context: server

library(data.table)
library(tidyquant)
library(ggplot2)
library(plotly)
output$value <- renderText({ input$stock })

selectedData <- reactive({
  
    dt_stock <- data.table(tq_get(input$stock, get = "stock.prices", from = input$dates[1], 
                                  to = input$dates[2]))
  })

output$distPlot <- renderPlotly({
  
  g <- ggplot(data = selectedData(), aes(x = date, y = close)) +
    geom_line() + theme_tq()
  ggplotly(g)

})
```

